\documentclass[11pt,a4paper]{article}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{xcolor}

\newcommand{\R}{\mathbb{R}}

\begin{document}
	
	\title{\textbf{EngageNet Draft}}
	\author{Lado Turmanidze}
	\date{April 20, 2026}
	\maketitle
	
	\section{Architecture}
	\subsection{Input}
	Let $x=\{x_{1},\dots,x_{M}\}$ with $x_{i}\in\R^{C_{i}\times L}$ for all $i\in\{1,\dots,M\}$, where $C_{i}$ is the number of acquisition channels for the $i$-th modality and $L$ represents the number of time steps of the input signal.
	
	\subsection{Output}
	In \cite{ziyu2025}, $y$ is a discrete value corresponding to a category, which is then converted into a one-hot encoding $p(y|x)\in\R^{N}$ (where $N$ is the number of categories). In our case, since we are performing regression, $y\in[0,1] \implies p(y|x)\in[0,1]^{N}$, so our model outputs the predicted category probability $p(\hat{y}|x)\in[0,1]^{N}$.
	
	\subsection{Inner Workings}
	We need to capture contextual information from physiological time series simultaneously, and a unidirectional approach cannot fully capture the complex temporal patterns. The multimodal BiMamba network consists of two modules: the intra-modal BiMamba module and the inter-modal BiMamba module. The former is designed to model each modality independently, while the latter effectively fuses multimodal features.
	
	\subsubsection{Intra-modal BiMamba Module}
	First, an initial encoder $h_{i} = \text{InitEncoder}_{i}(x_{i}) \in \R^{L^{\prime}\times C_{i}^{\prime}}$ for all $i\in\{1,\dots,M\}$ is used to extract shallow features from a specific modality, where $C_{i}^{\prime}$ is the number of output channels and $L^{\prime}$ is the feature length of the output signal. 
	
	The transposition of dimensions from $C_i \times L$ to $L^{\prime} \times C_i^{\prime}$ physically aligns the data structure with the sequence-first requirement of autoregressive models. By enforcing the sequence length $L^{\prime}$ as the primary operational dimension, the subsequent state-space and 1D convolutional operators can process the temporal dimension across the channel feature space.
	
	The BiMamba module operates as follows:
	\begin{enumerate}
		\item The output of the gating mechanism is $g_{i}=\sigma(W_{i}^{g}h_{i}+b_{i}^{g})$, where $h_{i}$ is the hidden state, $W_{i}^{g}$ is the weight matrix, $b_{i}^{g}$ is the bias, and $\displaystyle \sigma(x)=x\cdot\frac{1}{1+e^{-x}}$ (SiLU). Intuitively, $g_{i}$ highlights emotion-relevant information while suppressing noise and redundancy.
		
		\item BiMamba models temporal dependencies from both forward and backward perspectives using state-space modeling, thereby capturing richer contextual dynamics:
		$$h_{i}^{\rightarrow}=g_{i}\otimes \text{SSM}_{\rightarrow}(\sigma(\text{Conv1D}_{\rightarrow}(W_{i}^{h}h_{i}+b_{i}^{h})))\in\R^{L^{\prime}\times C_{i}^{\prime}}$$
		$$h_{i}^{\leftarrow}=g_{i}\otimes \text{SSM}_{\leftarrow}(\sigma(\text{Conv1D}_{\leftarrow}(\text{Rev}_{t}(W_{i}^{h}h_{i}+b_{i}^{h}))))\in\R^{L^{\prime}\times C_{i}^{\prime}}$$
		where $h_{i}^{\rightarrow}$ and $h_{i}^{\leftarrow}$ are the feature representations of the $i$-th modality in forward and backward modeling. $\text{Rev}_{t}(\cdot)$ denotes flipping along the time dimension $L^{\prime}$.
		
		The operator $\otimes$ denotes the Hadamard product (element-wise multiplication), which explains why the dimensions remain strictly unchanged, unlike a direct sum ($\oplus$) or tensor product. $W_{i}^{h}$ represents the weight matrix and $b_{i}^{h}$ represents the bias. 
		
		$\text{SSM}(\cdot)$ represents the Selective State Space Model. Formally, it maps a 1-dimensional sequence through a continuous linear time-invariant (LTI) system defined by the state equation $x'(t) = A x(t) + B u(t)$ and output $y(t) = C x(t)$. To operate on discrete sequence steps, the continuous transition operator $A$ and input operator $B$ are discretized via a timescale parameter $\Delta$, yielding the discrete operators $\bar{A} = \exp(\Delta A)$ and $\bar{B} = (\Delta A)^{-1}(\bar{A} - I)\Delta B$. 
		
		Unlike traditional LTI systems, Mamba introduces \textit{selection} by making the discretized parameters $(\bar{B}, C, \Delta)$ functions of the input $u_t$. Specifically:
		$$ \Delta_t = \text{softplus}(s_{\Delta} + \text{Linear}(u_t)) $$
		$$ B_t = \text{Linear}(u_t), \quad C_t = \text{Linear}(u_t) $$
		where $s_{\Delta} \in \mathbb{R}^{D}$ is a learned, input-independent bias term that defines the baseline timescale of the system. The inclusion of $s_{\Delta}$ within the \textit{softplus} function ensures that the resulting $\Delta_t$ remains strictly positive, which is required for the stability of the discretization. This selection mechanism allows the discrete transition $x_t = \bar{A}_t x_{t-1} + \bar{B}_t u_t$ to dynamically adjust its temporal resolution - effectively allowing the model to "reset" its state or focus on transient patterns based on the specific content of the sequence $u_t$.
		
		\item BiMamba applies a linear projection and a  \hypertarget{residual}{\textcolor{red}{residual connection}} to integrate bidirectional features and stabilize training:
		$$u_{i}=h_{i}+\left(W_{i}^{o}\left(\frac{h_{i}^{\rightarrow}+\text{Rev}_{t}(h_{i}^{\leftarrow})}{2}\right)+b_{i}^{o}\right)\in\R^{L^{\prime}\times C_{i}^{\prime}}$$
		which is the output of the intra-modal BiMamba module for the $i$-th modality. $W_{i}^{o}$ is the weight matrix, and $b_{i}^{o}$ is the bias.
	\end{enumerate}
	
	\subsubsection{Inter-modal BiMamba Module}
	Relying solely on intra-modal modeling neglects inter-modal correlations that are crucial for comprehensive multimodal understanding. Let the concatenation along the channel dimension be denoted by the operator $\circ$. We define the concatenated intermediate matrix $U$:
	$$U = u_1 \circ u_2 \circ \dots \circ u_M$$
	where $U \in \R^{L^{\prime} \times \sum_{i=1}^{M} C_i^{\prime}}$. To enable state-space modeling across the modalities rather than the temporal space, we transpose this matrix:
	$$m = U^{\top} = \text{Transpose}(u_1 \circ u_2 \circ \dots \circ u_M) \in \R^{(\sum C_i^{\prime}) \times L^{\prime}}$$
	Thus, each time step acts structurally as a "channel," while the concatenated modality dimension serves as the sequence length. We then input $m$ into a BiMamba structure:
	$$ H = \text{BiMamba}(m) \in \R^{\sum_{i=1}^{M} C_i^{\prime} \times L^{\prime}} $$ By performing bidirectional state modeling along the fused $\sum_{i=1}^{M} C_i^{\prime}$ axis, the sequence transition operators effectively treat preceding modalities as the context basis for subsequent modalities.
	
	The function $H = \text{BiMamba}(m)$ represents the application of the entire bidirectional Mamba block (All 1--3 steps of the intra-modal module above) to the fused matrix $m$. In this inter-modal stage, the "sequence length" is now the total number of concatenated channels $\sum C_i^{\prime}$, and the "features" at each step are the temporal points $L^{\prime}$. This allows the model to build a context where the state of one modality can directly influence the hidden state of another.
	
	In the forward process, the hidden states built from modalities $\{1, \dots, i- 1 \}$, while in the backward process the hidden states derived from the modalities $\{M, M - 1, \dots, i + 1\}$ provide additional temporal information for the $i$-th modality.
	
	\section{Possible Improvement Ideas}
	\begin{enumerate}
		\item \hyperlink{residual}{Residual connection}: we can replace the standard residual connection with DeepSeek AI's Manifold-Constrained Hyper-Connections (mHC) \cite{xie2026mhc}. 
		
		Let the BiMamba transformation block be denoted as the layer function $$ \mathcal{F}(h_i) = W_{i}^{o}\left(\frac{h_{i}^{\rightarrow}+\text{Rev}_{t}(h_{i}^{\leftarrow})}{2}\right)+b_{i}^{o} $$ In the original architecture, the (residual) update is $u_i = h_i + \mathcal{F}(h_i) $. 
		
		To apply mHC, we expand the residual stream width by a factor of $n$ to form a multi-stream representation $\mathbf{h}_i \in \R^{n \times L^{\prime} \times C_i^{\prime}}$. The update rule becomes:
		$$u_i = \mathcal{H}_i^{res} \mathbf{h}_i + (\mathcal{H}_i^{post})^{\top} \mathcal{F}(\mathcal{H}_i^{pre} \mathbf{h}_i)$$
		where $\mathcal{H}_i^{pre} \in \R^{1 \times n}$ aggregates the multi-stream into a single input for $\mathcal{F}$, $\mathcal{H}_i^{post} \in \R^{1 \times n}$ maps the output back to the stream, and $\mathcal{H}_i^{res} \in \R^{n \times n}$ mixes features within the stream. 
		
		The structural mappings $\mathcal{H}_i^{pre}$ and $\mathcal{H}_i^{post}$ are composed of dynamic, input-dependent linear projections and static, learnable biases. To prevent signal cancellation, they are mapped through a \textit{sigmoid} activation $\sigma$:
		
		$$\mathcal{H}_i^{pre} = \sigma(\alpha_{i}^{pre} (\vec{\mathbf{h}}_i \varphi_{i}^{pre}) + b_{i}^{pre})$$
		
		$$\mathcal{H}_i^{post} = 2\sigma(\alpha_{i}^{post} (\vec{\mathbf{h}}_i \varphi_{i}^{post}) + b_{i}^{post})$$
		
		where $\vec{\mathbf{h}}_i$ is the flattened input tensor, $\varphi$ represents the linear projection weights, and $\alpha$ acts as a learnable gating factor.
		
		To maintain signal conservation, $\mathcal{H}_i^{res}$ is projected onto the Birkhoff polytope using the Sinkhorn-Knopp algorithm. The Birkhoff polytope is the convex hull of all permutation matrices, consisting entirely of doubly stochastic matrices (square matrices with non-negative real entries where each row and column sums exactly to 1). 
		
		The projection is achieved iteratively:
		$$\mathcal{H}_i^{res} = \text{Sinkhorn-Knopp}(\tilde{\mathcal{H}}_i^{res})$$
		Given an initial positive matrix $M^{(0)} = \exp(\tilde{\mathcal{H}}_i^{res})$, the Sinkhorn-Knopp algorithm alternately normalizes the rows and columns until convergence. Constraining $\mathcal{H}_i^{res}$ to the Birkhoff polytope ensures its spectral norm is strictly bounded by 1 ($||\mathcal{H}_i^{res}||_2 \le 1$). This property guarantees stability across deep layers, strictly regulating the vector norm and preventing the signal from exploding or vanishing within the Hilbert space of our feature representations.
	\end{enumerate}
	
	\begin{thebibliography}{9}
		
		\bibitem{ziyu2025}
		Ziyu Jia et al., \emph{A Multimodal BiMamba Network with Test-Time Adaptation for Emotion Recognition Based on Physiological Signals}, 39th Conference on Neural Information Processing Systems (NeurIPS 2025).
		
		\bibitem{xie2026mhc}
		Zhenda Xie et al., \emph{mHC: Manifold-Constrained Hyper-Connections}, arXiv preprint arXiv:2512.24880v2 (2026).
		
	\end{thebibliography}
	
\end{document}